---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# covid19Tracker

<!-- badges: start -->
<!-- badges: end -->

The goal of covid19Tracker is to facilitate exploration of Coronavirus disease (COVID-19) dataset. The dataset is provided by [JHU CSSE COVID-19 Data](https://github.com/CSSEGISandData/COVID-19) and is updated everyday.

The dataset includes new cases, cumulative cases, new deaths and cumulative deaths for each day. It also contains geographical coordinates(Lat,Long) for each country.

This package provide functions to:

+ View full dataset in a tidy format
+ Plot total cases between a selected period of time on the world map
+ Plot daily cases of a specific country between a selected period of time

## Installation

<!-- You can install the released version of covid19Tracker from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("covid19Tracker") -->
<!-- ``` -->

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("PlasterPate/covid19Tracker")
```
## Examples

### Getting data

```{r example1}
library(covid19Tracker)
dataset <- fetchData()
head(dataset)
```

### Visualising data
```{r echo=FALSE}
options(scipen = 999)
```

```{r example2, message=FALSE, warning=FALSE, error=FALSE}
library(covid19Tracker)
plotWorldMap(dateRange = c("2020-09-01", "2020-09-30"), type = "Confirmed")
```

```{r example3}
library(covid19Tracker)
plotCountryTimeline(dateRange = c("2020-01-01", "2020-12-29"), country = "Iran")
```




