---
title: "How to use covid19Tracker"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{covid19Tracker}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(covid19Tracker)
```

```{r echo=FALSE}
options(scipen = 999)
```

## Geting Data
#### You can get full data by simply calling *fetchData()*. it returns a dataframe. Each row contains information of a single country in a single day.


#### Columns are:

+ **Region**: Name of the country
+ **Date**: Day of observation. Date is in format "yyyy-mm-dd" or "yyyy/mm/dd"
+ **CumConfirmed**: Total number of confirmed cases until this day
+ **Confirmed**: Number of new confirmed cases in this day
+ **CumDeath**: Total number of death cases until this day
+ **Death**: Number of new death cases in this day
+ **Lat**: Latitude of the country on map
+ **Long**: Longitude of the country on map
      
```{r fetchData}
dataset <- fetchData()
tail(dataset)
```

#### You can view list of all countrie that you can pass to plotCountryTimeline()

```{r countries}
unique(dataset$Region)
```
      
## Visualizing Data 
#### You can plot a choropleth map of world with *plotWorldMap()*. This function has two arguments:

* **dateRange**: A vector of length 1 or 2 containing date strings. If you pass one date, a plot is drawn for that specific day. If you pass two dates, a plot is drawn for days between these two day.(first and last day wich are passed, are included). Proper formats of date is "yyyy-mm-dd" and "yyyy/mm/dd"

* **type**: A string indicating the case of infected person. Can be one of "Confirmed" or "Death"

#### An example with one date
```{r world1, message=FALSE, warning=FALSE, error=FALSE, fig.width=7}
dateRange = c("2020-08-23")
type = "Death"
plotWorldMap(dateRange, type)
```
 
#### An example with two dates
```{r world2, message=FALSE, warning=FALSE, error=FALSE, fig.width=7}
dateRange = c("2020-08-23", "2020-08-24")
type = "Confirmed"
plotWorldMap(dateRange, type)
```
      
